A spatial analysis of the environmental correlates of COVID-19 incidence in Spain

### 2020-04-19 Environmental-Correlates-of-COVID19-Spain/Environmental-Correlates-of-COVID19-Spain.tex
Finished editing sections Data and Methods and improved the plots for the results

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={A spatial analysis of the environmental correlates of COVID-19 incidence in Spain},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

Our dataset includes information about the daily number of cases of
COVID-19 reported in Spain at the provincial level (NUTIII in Eurostat
terminology) for the period between March 13th and April 11th,
inclusive. For our purposes, we consider positive cases reported, but
excluding symptomatic cases diagnosed by a doctor without a Polymerase
Chain Reaction (PCR) test. The Spanish National Government publishes
periodic updates at the regional level (NUTII) and the information is
also released at the provincial level as part of a collaborative project
{[}\textbf{by whom?}{]}. This information is compiled from several
sources, mainly the official web pages of the Spanish regional
goverments. In addition, we consider two sets of explanatory variables.
The first one, and the focus of this research, is set of two
environmental variables, namely temperature and humidity, which are
collected from official sources (i.g., AEMET, the state meteorology
agency, and MAPA, the ministry of agriculture, fisheries, and food). The
second set provides some relevant controls for multivariate analysis,
and refers to economic and demographic attributes of the province (also
collected from official sources, i.e., INE, the national statistics
institute). Table \ref{tab:descriptive-statistics} shows the descriptive
statistics and the provenance of the data.

@@

\caption{\label{tab:descriptive-statistics}\label{tab:descriptive-statistics} Descriptive statistics}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{15em}rrrr>{\raggedright\arraybackslash}p{5em}}
\toprule
Variable & Note & Min & Mean & Max & SD & Source\\
\midrule
\rowcolor{gray!6}  COVID-19 Incidence & Incidence in reported cases of SARS-19 per 100,000 people & 0.38 & 153.61 & 1149.36 & 186.23 & Montera34\\
Area & Area of province in sq.km & 1978.12 & 10118.79 & 21767.93 & 4.77 & INE\\
\rowcolor{gray!6}  GDPpc & GDP per capita in €1,000s & 16.67 & 22.51 & 36.00 & 4805.98 & INE\\
Older & Percentage of people aged 65 and older in the province & 15.16 & 21.03 & 31.36 & 3.95 & INE\\
\rowcolor{gray!6}  Population Density & Population density in the province in people per sq.km & 8.60 & 140.04 & 829.76 & 181.25 & INE\\
\addlinespace
Mean Temperature & Mean temperature in province by date, in C & 1.00 & 12.18 & 23.20 & 3.67 & AEMET\\
\rowcolor{gray!6}  Humidity & Relative humidity in province by date & 2.00 & 77.82 & 100.00 & 10.37 & MAPA\\
\bottomrule
\multicolumn{7}{l}{\textit{Note: }}\\
\multicolumn{7}{l}{Montera34: https://code.montera34.com:4443/numeroteca/covid19/-/blob/master/README\_providencialdata19.md}\\
\multicolumn{7}{l}{INE (Instituto Nacional de Estadistica): https://www.ine.es/}\\
\multicolumn{7}{l}{AEMET (Agencia Estatal de Meteorologia): http://eportal.mapa.gob.es}\\
\multicolumn{7}{l}{MAPA (Ministerio de Agricultura, Pesca y Alimentacion): http://eportal.mapa.gob.es}\\
\end{tabular}}
\end{table}

@@

where \(\bf{Y}\) is now a vector of dimension \(NT \times 1\),
\(\bf{X}\) is a block-diagonal matrix \(NT \times K\) (with
\(K = \sum_t{k_t}\)) and \(\epsilon\) is a \(NT \times 1\) vector. Using
the Kronecker product notation (\(\otimes\)), the error matrix structure
is expressed concisely as:

@@

\noindent where \(\bf{A} =I_{TN}-\bf{\Gamma} \otimes W\) with
\(\bf{\Gamma} = diag(\rho_1, \cdots, \rho_T)\).

This specification assumes that incidence in a province (\(y_{st}\)) at
time \(t\) is partially determined by the weighted average (\(Wy_{st}\))
of incidence in neighbouring provinces. Coefficients for the spatially
lagged variable are estimated for each time period \(\rho_t\) and
identifies the intensity and the sign of the impacts of neighbourhood.
It is possible test the null hypothesis of identtical levels of spatial
dependence (\(\rho_i=\rho_j, \forall i,j\)). The correspond Wald test is
available in the \texttt{R} package \texttt{spsur}.

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/delta-time-1.pdf}
\caption{\label{fig:delta-time}Temporal evolution of spatial
autocorrelation coefficient}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/beta-intercept-time-1.pdf}
\caption{\label{fig:beta-intercept-time}Temporal evolution of intercept}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/beta-density-time-1.pdf}
\caption{\label{fig:beta-density-time}Temporal evolution of coefficient
for log(Density)}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/beta-transit-time-1.pdf}
\caption{\label{fig:beta-transit-time}Temporal evolution of coefficient
for Transit}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/beta-humidity-time-1.pdf}
\caption{\label{fig:beta-humidity-time}Temporal evolution of coefficient
for log(Humidity)}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/beta-temperature-time-1.pdf}
\caption{\label{fig:beta-temperature-time}Temporal evolution of
coefficient for log(Temperature)}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/beta-sunshine-time-1.pdf}
\caption{\label{fig:beta-sunshine-time}Temporal evolution of coefficient
for log(Sunshine + 0.1)}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Wsur <-}\StringTok{ }\KeywordTok{as}\NormalTok{(spdep}\OperatorTok{::}\KeywordTok{listw2mat}\NormalTok{(listw), }\StringTok{"CsparseMatrix"}\NormalTok{)}
\NormalTok{trsur <-}\StringTok{ }\NormalTok{spatialreg}\OperatorTok{::}\KeywordTok{trW}\NormalTok{(Wsur, }\DataTypeTok{type =} \StringTok{"MC"}\NormalTok{)}
\NormalTok{impacts.sur.slm_lag11 <-}\StringTok{ }\KeywordTok{impactspsur}\NormalTok{(sur.slm_lag11, }\DataTypeTok{tr =}\NormalTok{ trsur,}\DataTypeTok{R =} \DecValTok{1000}\NormalTok{)}

\NormalTok{impacts.sur.slm_lag11[[}\DecValTok{1}\NormalTok{]]}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Impact measures (lag, trace):
##                                       Direct   Indirect      Total
## log(GDPpc)_1                       0.6736035  0.6395634  1.3131669
## log(Older)_1                      -0.8002302 -0.7597912 -1.5600214
## log(Density)_1                     0.1662437  0.1578427  0.3240864
## Transit_1                          0.3413888  0.3241370  0.6655259
## log(Humidity_lag11)_1             -1.5578465 -1.4791220 -3.0369685
## log(Mean_Temp_lag11)_1            -1.7365494 -1.6487943 -3.3853437
## log(Sunshine_Hours_lag11 + 0.1)_1 -0.2804735 -0.2663000 -0.5467734
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{impacts.sur.slm_lag11[[}\DecValTok{2}\NormalTok{]]}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Impact measures (lag, trace):
##                                        Direct    Indirect      Total
## log(Density)_2                     0.06248795  0.04048188  0.1029698
## Transit_2                          0.44006548  0.28508982  0.7251553
## log(Humidity_lag11)_2             -1.06244958 -0.68829202 -1.7507416
## log(Mean_Temp_lag11)_2            -1.47760442 -0.95724386 -2.4348483
## log(Sunshine_Hours_lag11 + 0.1)_2 -0.19072953 -0.12356126 -0.3142908
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{impacts.sur.slm_lag11[[}\DecValTok{3}\NormalTok{]]}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Impact measures (lag, trace):
##                                        Direct    Indirect       Total
## log(Density)_3                     0.02426235  0.01927572  0.04353807
## Transit_3                          0.43033000  0.34188455  0.77221455
## log(Humidity_lag11)_3             -0.97379005 -0.77364759 -1.74743764
## log(Mean_Temp_lag11)_3            -1.39450981 -1.10789707 -2.50240689
## log(Sunshine_Hours_lag11 + 0.1)_3 -0.09683377 -0.07693158 -0.17376535
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{myimpact <-}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DataTypeTok{ncol =} \DecValTok{5}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{29}\NormalTok{)}
\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{2}\OperatorTok{:}\DecValTok{30}\NormalTok{)\{}
\NormalTok{  myimpact[i}\DecValTok{-1}\NormalTok{,] <-}\StringTok{ }\NormalTok{impacts.sur.slm_lag11[[i]]}\OperatorTok{$}\NormalTok{res}\OperatorTok{$}\NormalTok{direct}
\NormalTok{\}}
\KeywordTok{matplot}\NormalTok{(myimpact, }\DataTypeTok{type=}\StringTok{'l'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/impacts-1.pdf}

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={A spatial analysis of the environmental correlates of COVID-19 incidence in Spain},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

Our dataset includes information about the daily number of cases of
COVID-19 reported in Spain at the provincial level (NUTIII in Eurostat
terminology) for the period between March 13th and April 11th,
inclusive. For our purposes, we consider positive cases reported, but
excluding symptomatic cases diagnosed by a doctor without a Polymerase
Chain Reaction (PCR) test. The Spanish National Government publishes
periodic updates at the regional level (NUTII) and the information is
also released at the provincial level as part of a collaborative project
by geovoluntarios.com\footnote{https://www.geovoluntarios.org/},
ProvidencialData19\footnote{https://www.datoscovid.es/pages/providencialdata19},
and ESRI España. This information is compiled from several sources,
mainly the official web pages of the Spanish regional goverments, as
documented in Centro de Datos
Covid-19\footnote{https://www.datoscovid.es/pages/sobre-la-iniciativa}.
In addition, we consider two sets of explanatory variables. The first
one, and the focus of this research, is set of two environmental
variables, namely temperature and humidity, which are collected from
official sources (i.g., \emph{AEMET}, the state meteorology agency, and
\emph{MAPA}, the ministry of agriculture, fisheries, and food). The
second set provides some relevant controls for multivariate analysis,
and refers to economic and demographic attributes of the province (also
collected from official sources, i.e., INE, the national statistics
institute). Table \ref{tab:descriptive-statistics} shows the descriptive
statistics and the provenance of the data.

@@

\caption{\label{tab:descriptive-statistics}\label{tab:descriptive-statistics} Descriptive statistics}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{15em}rrrr>{\raggedright\arraybackslash}p{5em}}
\toprule
Variable & Note & Min & Mean & Max & SD & Source\\
\midrule
\rowcolor{gray!6}  COVID-19 Incidence & Incidence in reported cases of SARS-19 per 100,000 people & 0.38 & 153.61 & 1149.36 & 186.23 & ProvidencialData19\\
Area & Area of province in sq.km & 1978.12 & 10118.79 & 21767.93 & 4.77 & INE\\
\rowcolor{gray!6}  GDPpc & GDP per capita in €1,000s & 16.67 & 22.51 & 36.00 & 4805.98 & INE\\
Older & Percentage of people aged 65 and older in the province & 15.16 & 21.03 & 31.36 & 3.95 & INE\\
\rowcolor{gray!6}  Population Density & Population density in the province in people per sq.km & 8.60 & 140.04 & 829.76 & 181.25 & INE\\
\addlinespace
Mean Temperature & Mean temperature in province by date, in C & 1.00 & 12.18 & 23.20 & 3.67 & AEMET\\
\rowcolor{gray!6}  Humidity & Relative humidity in province by date & 2.00 & 77.82 & 100.00 & 10.37 & MAPA\\
\bottomrule
\multicolumn{7}{l}{\textit{Note: }}\\
\multicolumn{7}{l}{ProvidencialData19: https://www.datoscovid.es/pages/providencialdata19}\\
\multicolumn{7}{l}{INE (Instituto Nacional de Estadistica): https://www.ine.es/}\\
\multicolumn{7}{l}{AEMET (Agencia Estatal de Meteorologia): http://eportal.mapa.gob.es}\\
\multicolumn{7}{l}{MAPA (Ministerio de Agricultura, Pesca y Alimentacion): http://eportal.mapa.gob.es}\\
\end{tabular}}
\end{table}

@@

\noindent where \(\bf{Y}\) is now a vector of dimension \(NT \times 1\),
\(\bf{X}\) is a block-diagonal matrix \(NT \times K\) (with
\(K = \sum_t{k_t}\)) and \(\epsilon\) is an \(NT \times 1\) vector.
Using the Kronecker product notation (\(\otimes\)), the error matrix
structure is expressed concisely as:

@@

\noindent where \(\bf{A} =I_{TN}-\bf{\Gamma} \otimes W\) is the
spatially lagged dependent variable, and
\(\bf{\Gamma} = diag(\rho_1, \cdots, \rho_T)\).

This specification assumes that outcome (\(y_{st}\)) at location \(s\)
and time \(t\) is partially determined by the weighted average
(\(Wy_{st}\)) of the outcome in neighboring provinces, with neighborhood
defined by matrix \(W\) of spatial weights. In other words, the
spatially lagged dependent variable represents a process of contagion,
where the disease in neighboring provinces can spillover in a spatial
way. The coefficients of the spatially lagged variable are estimated for
each time period \(\rho_t\) and identify the intensity and the sign of
the contagion effect. It is possible test the null hypothesis of
identical levels of spatial dependence (\(\rho_i=\rho_j, \forall i,j\)).
The correspond Wald test is available in the \texttt{R} package
\texttt{spsur}.

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/delta-time-1.pdf}
\caption{\label{fig:delta-time}Temporal evolution of the spatial
autocorrelation coefficient; dots are the point estimates and vertical
lines are 95\% confidence intervals. In yellow is the period after the
declaration of the state of emergency, and in orange is the period when
only essential activities were allowed.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/beta-intercept-time-1.pdf}
\caption{\label{fig:beta-intercept-time}Temporal evolution of intercept;
dots are the point estimates and vertical lines are 95\% confidence
intervals. In yellow is the period after the declaration of the state of
emergency, and in orange is the period when only essential activities
were allowed.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/beta-density-time-1.pdf}
\caption{\label{fig:beta-density-time}Temporal evolution of coefficient
for log(Density); dots are the point estimates and vertical lines are
95\% confidence intervals. In yellow is the period after the declaration
of the state of emergency, and in orange is the period when only
essential activities were allowed.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/beta-transit-time-1.pdf}
\caption{\label{fig:beta-transit-time}Temporal evolution of coefficient
for Transit; dots are the point estimates and vertical lines are 95\%
confidence intervals. In yellow is the period after the declaration of
the state of emergency, and in orange is the period when only essential
activities were allowed.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/beta-humidity-time-1.pdf}
\caption{\label{fig:beta-humidity-time}Temporal evolution of coefficient
for log(Humidity); dots are the point estimates and vertical lines are
95\% confidence intervals. In yellow is the period after the declaration
of the state of emergency, and in orange is the period when only
essential activities were allowed.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/beta-temperature-time-1.pdf}
\caption{\label{fig:beta-temperature-time}Temporal evolution of
coefficient for log(Temperature); dots are the point estimates and
vertical lines are 95\% confidence intervals. In yellow is the period
after the declaration of the state of emergency, and in orange is the
period when only essential activities were allowed.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Environmental-Correlates-of-COVID19-Spain_files/figure-latex/beta-sunshine-time-1.pdf}
\caption{\label{fig:beta-sunshine-time}Temporal evolution of coefficient
for log(Sunshine + 0.1); dots are the point estimates and vertical lines
are 95\% confidence intervals. In yellow is the period after the
declaration of the state of emergency, and in orange is the period when
only essential activities were allowed.}
\end{figure}
